BetweenExpDifferences

### 2016-01-27 analysis/BetweenExpDifferences.Rmd
outputting raw literal listener and pramatic listener combined data sets

@@

## Visulaziations?
```{r}
# ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
#   geom_point(alpha = 0.5) +
#   geom_jitter(width = 0.1, height = 0.1) +
#   facet_wrap(~scale + exp)
```

@@

>>>>

### Save literalListenerData
```{r}
# write.csv(allL0Listener, "/Users/benpeloquin/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
```

@@

## Visulaziations?
```{r}
```

@@

### Save literalListenerData
```{r}
# write.csv(allL1Listener, "/Users/benpeloquin/Desktop/Projects/scalar_implicature/models/model_data/RawPragmaticListenerCombined.csv")
```
